Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Paper restructure
Comments

@@

\maciek{REALLY bad name. Both the learning problem and the general one is online.}

@@

@@

@@

@@

>>>>

\maciek{TODO: discuss the title. We should not claim tight bounds with an exponential gap. Reviewers will point this out, as this is an easy thing to criticize in the review.}

@@

\maciek{Not precise name? Both the learning problem and the general one is online.}

\maciek{Start with referencing the table of results, saying that some results are known already. And really emphasize here that we now have an improved lower bound from the previous section, as that model was a subproblem.}

@@

\maciek{Better name than DET?}

@@

\maciek{I'll write it some day. Maciek.}

\subsection{Costly reconfiguration example}

\maciek{A linear path in reconfiguration graph.}

@@

\maciek{Intro: compare to previous algorithm. Note strict competitive ratio vs large additive term.}

@@

\section{Note on distributed algorithms}

\maciek{How to distribute our algorithms: PPL, k=2 and DET}
